\bf On semidefinite-representable sets over valuation fields

### 2025-03-17 article/paper_padic_spec.tex
commit by Simone

\begin{proposition}
  Let $\PP \subset K^n$ be a polyhedron and $f : K^n \to K^n$ be a linear mapping.
  If $f \in \GL_n(\OK)$ or if there exists $\lambda_1, \dots, \lambda_n \in K$ such that 
  $(x_1,\dots,x_{n-1}, x_n) \mapsto (x_1,\dots, x_{n-1})$.
\end{proposition}

@@

The two above results allows us to demonstrate the following proposition, which we will use to prove the general case.

>>>>

\begin{proposition}\simone{l'enoncé est incomplet}
  Let $P \subset K^n$ be a polyhedron and let $f : K^n \to K^n$ be a linear mapping.
  If $f \in \GL_n(\OK)$ or if there exists $\lambda_1, \dots, \lambda_n \in K$ such that
  $(x_1,\dots,x_{n-1}, x_n) \mapsto (x_1,\dots, x_{n-1})$.
\end{proposition}

@@

The two above results\footnote{\simone{il y en an un}}
allows us to demonstrate the following proposition, which we will use to prove the general case.
